Memory-efficient Mixed-Precision Implementations for\\Robust Explicit MPC

### 2019-04-08 emsoft-2019/RMPC_Daisy.tex
seperating 3.1 and 3.2

where $\mathcal U$ and $\mathcal X$ are polyhedral sets as feasible sets of inputs and states. $Q\in\reals^{n\times n}$, $R\in\reals^{m\times m}$ and $Q_F\in\reals^{n\times n}$ are positive semidefinite matrices and $N$ denotes the length of prediction horizon.
\begin{theorem}[\Sadegh{add reference}]
The optimization  \eqref{eq:RMPC_prob} can be translated into a multi-parametric quadratic problem which admits a closed-form solution $U_N=K(x_0)$. Furthermore, for the case that $Q\geq0$, $Q_F\geq0$ and $R>0$, the controller $K$ is a continuous piecewise affine (PWA) function over polyhedral regions:
\begin{equation}
K(x_k)=
\begin{cases}
F_1x_k+G_1 & \text{if $x_k\in \mathcal{R}_1$}\\
F_2x_k+G_2 & \text{if $x_k\in \mathcal{R}_2$}\\
\vdots\\
F_Px_k+G_P & \text{if $x_k\in \mathcal{R}_P$}
\end{cases} 
\end{equation}
where $\mathcal{R}_i$ is a ploytope determined by a set of linear inequalities $\mathcal R_i = \{x\in\mathcal X\,|\,H_ix\leq K_i\}$. 
\end{theorem}
The essential idea of this theorem is to utilize the closed form $x_i=A^ix_0+\sum_{l=0}^{i-1}A^{i-l-1}Bu_l$ and .... 
\Sadegh{What is a multi-parametric quadratic problem? Not defined.}

\Sadegh{Adding a remark and saying that the approach works as long as the solution of formulated optimization has a piecewise affine form?}

@@

To keep the costs of implementation down, low-end microcontrollers usually have limited memory and computational power. Therefore, implementation of the above explicit MPC on microcontrollers will bring some issues since all regions' matrices ($H_i$s and $K_i$s) and activation functions ($F_i$s and $G_i$s) have to be stored on the microcontroller. The goal of our paper is present an approach for minimizing the memeory usage of the implementation while satisfying the hard constraints on the states.

\section{Finite Precision Implementation}
\Sadegh{To be included by Rocco}

>>>>

where $\mathcal U$ and $\mathcal X$ are polyhedral sets as feasible sets of inputs and states. $Q\in\reals^{n\times n}$, $R\in\reals^{m\times m}$ and $Q_F\in\reals^{n\times n}$ are positive semidefinite matrices and $N$ denotes the length of prediction horizon.
\begin{theorem}[\Sadegh{add reference}]
The optimization  \eqref{eq:RMPC_prob} can be translated into a multi-parametric quadratic problem which admits a closed-form solution $U_N=K(x_0)$. Furthermore, for the case that $Q\geq0$, $Q_F\geq0$ and $R>0$, the controller $K$ is a continuous piecewise affine (PWA) function over polyhedral regions:
\begin{equation}
K(x_k)=
\begin{cases}
F_1x_k+G_1 & \text{if $x_k\in \mathcal{R}_1$}\\
F_2x_k+G_2 & \text{if $x_k\in \mathcal{R}_2$}\\
\vdots\\
F_Px_k+G_P & \text{if $x_k\in \mathcal{R}_P$}
\end{cases} 
\end{equation}
where $\mathcal{R}_i$ is a ploytope determined by a set of linear inequalities $\mathcal R_i = \{x\in\mathcal X\,|\,H_ix\leq K_i\}$. 
\end{theorem}
The essential idea of this theorem is to utilize the closed form $x_i=A^ix_0+\sum_{l=0}^{i-1}A^{i-l-1}Bu_l$ of the following form:
\begin{align}
	&\min_{U_N}U_N^TZU_N+x_0^TVU_N+x_0^TYx_0\nonumber\\
	&s.t.\quad JU_N\leq s+Dx_0
\end{align} 
where, $Z\in \reals^{mN\times mN}$, $V\in\reals^{n\times mN}$, $Y\in\reals^{n\times n}$, $J\in\reals^{q\times mN}$, $s\in\reals^{q}$, $D\in\reals^{q\times n}$ and $q$ is the number of inequalities.
%\Sadegh{What is a multi-parametric quadratic problem? Not defined.}

%\Sadegh{Adding a remark and saying that the approach works as long as the solution of formulated optimization has a piecewise affine form?}

@@

To keep the costs of implementation down, low-end microcontrollers usually have limited memory and computational power. Therefore, implementation of the above explicit MPC on microcontrollers will bring some issues since all regions' matrices ($H_i$s and $K_i$s) and activation functions ($F_i$s and $G_i$s) have to be stored on the microcontroller. The goal of our paper is present an approach for minimizing the memeory usage of the implementation while satisfying the hard constraints on the states. 
%\section{Finite Precision Implementation}
%\Sadegh{To be included by Rocco}
